Paper Visualization

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
new visuals

```{r How Many Topics}
library(ldatuning)

@@

```{r LDA Model}
# Run LDA model to find themes (adjust number of topics as needed)
set.seed(123) # Set seed for reproducibility
lda_model <- LDA(dtm, k = 5, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
```

>>>>

```{r How Many Topics, eval=FALSE, include=FALSE}
library(ldatuning)

@@

```{r LDA Model}
set.seed(123) # Set seed for reproducibility
lda_model <- LDA(dtm, k = 8, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
```
